ScipionBox: automatic processing for

### 2017-06-16 results.tex
after speaking with pablo
before start meassure results

\noindent
TODO (requires microscope time):
\begin{itemize}
   \item Check samba maximum speed between microscope PC and scipion box (IDEA: use DiskSpd o similar with no load in the computers, https://blogs.technet.microsoft.com/josebda/2014/10/13/diskspd-powershell-and-storage-performance-measuring-iops-throughput-and-latency-for-both-local-disks-and-smb-file-shares/)

@@

>>>>

\noindent
TODO (requires microscope time):
\begin{itemize}
   \item Check samba maximum speed between microscope PC and scipion box. We will use iperf since there is version for windows and linux.
   \begin{lstlisting}
        1) check network speed
        install  (may be iptraf also)
        Server -> iperf -s -p 80
        Client -> iperf -c server.cnb.csic.es -p 80

        2) meassure samba
        install Diskspd
        https://unhandled.wordpress.com/2016/07/20/madness-testing-smb-direct-network-throughput-with-diskspd/
        http://stealthpuppy.com/replicate-2015-folder-redirection-test/
        http://darklight.pro/using-microsoft-diskspd-to-test-starwind-virtual-san-storage-performance/
        (Compare local and remote storage)
        diskspd.exe -c2G -d120 -w100 -t1 (-o8) -b8K -h -L \\mb-win81\diskspd\testfile.dat
        -c -> file size
        -d -> time at least 120 (600 better)
        -w -> 100 write, 0 read
        -t -> threadas per file (1 or 2)
        -L -> capture latency information
        -h -> disable hardware, software cache 
        -b -> size of a read/write operation
        -o 	Outstanding I/Os (queue depth) per worker thread. Setting this higher increases the intensity of the test, which pushes your storage harder.??
    \end{lstlisting}

   \begin{lstlisting}
#smb.conf
   read raw = Yes
write raw = Yes
socket options = TCP_NODELAY IPTOS_LOWDELAY SO_RCVBUF=131072 SO_SNDBUF=131072
min receivefile size = 16384
use sendfile = true
aio read size = 16384
aio write size = 16384
    \end{lstlisting}
\begin{verbatim}
         OREALLY:
     TCP_NODELAY
Have the server send as many packets as necessary to keep delay low. This is
used on telnet connections to give good response time, and is used—some-
what counter-intuitively—to get good speed even when doing small requests
or  when  acknowledgments  are  delayed  (as  seems  to  occur  with  Microsoft
TCP/IP).  This  is  worth  a  30–50  percent  speedup  by  itself.  Incidentally,  in
Samba 2.0.4,
socket options = TCP_NODELAY
became the default value for
that option.
IPTOS_LOWDELAY
This is another option that trades off throughput for lower delay, but which
affects  routers  and  other  systems,  not  the  server.  All  the  IPTOS  options  are
new; they’re not supported by all operating systems and routers. If they are
supported, set
IPTOS_LOWDELAY
 whenever you set
TCP_NODELAY
.
SO_SNDBUF and SO_RCVBUF
The send and receive buffers can often be the reset to a value higher than that
of  the  operating  system.  This  yields  a  marginal  increase  of  speed  (until  it
reaches a point of diminishing returns).

read raw and write raw
These are important performance configuration options; they enable Samba to use
large reads and writes to the network, of up to 64KB in a single SMB request. They
also  require  the  largest  SMB  packet  structures,

\end{verbatim}

@@

   \item Report on project size

   \item what happens if I double size

   \item save raw data instead of corrected by the gain

   \item how to measure scipion overhead?????

   \item Laura backup in amazon and ctffind4
   \begin{lstlisting}
   rsync -aHAXxv --numeric-ids --delete --progress -e "ssh -T -c arcfour -o Compression=no -x" [source_dir] [dest_host:/dest_dir]
   \end{lstlisting}
   \begin{itemize}
    \item some preliminary tests with Laura
    \item no matter what machine we choose the network speed with CNB is 250 Mbits/s
    \item rsync report 25MB/seconds so there is not need to play here
    \item disk is ssd
    \item OS: Ubuntu 14.04, 8 CPUs 32GB, m4.2xlarge
    rsync -av --progress -e "ssh -i ~/Documents/CNB/Cloud/AWS/rmarabini.pem" VMImages/ScipionCloud-v1.1-beta.ova ubuntu@54.154.136.191:

#Comando iperf en server

sudo iperf -s -p 80

------------------------------------------------------------
Server listening on TCP port 80
TCP window size: 85.3 KByte (default)
------------------------------------------------------------
[  4] local 172.31.37.239 port 80 connected with 150.244.85.94 port 54796
[ ID] Interval       Transfer     Bandwidth
[  4]  0.0-10.0 sec   282 MBytes   236 Mbits/sec
[  5] local 172.31.37.239 port 80 connected with 150.244.85.94 port 54832
[  5]  0.0-10.1 sec   297 MBytes   247 Mbits/sec
[  4] local 172.31.37.239 port 80 connected with 150.244.85.94 port 55290
[  4]  0.0-40.1 sec  1.18 GBytes   253 Mbits/sec

#Comando iperf en client (copiar durante 40 sec)

iperf -c 54.154.136.191 -p 80 -t 40
